Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-07 report/report.tex
New title
Update abstract and background. Include results from collision run

\title{Footpath Planning for Example-driven Procedural Road Networks}

@@

This project assesses the feasibility of creating a 3D representation of geodata with the inclusion of pedestrian footpaths.
\\
Procedural modeling of road networks and even entire cities is of interest to the fields of urban planning and urban architecture.
In recent years, there have been an advent of tools that extract geodata from OpenStreetMap (OSM) and generate 3D representations of real world locations by placing terrain, buildings, roads and other features.
However, freely available such tools seldom include smaller roads and pedestrian footpaths such as walkways, sidewalks or trails.
\\
This project assesses the feasibility of creating such a service, by focusing on OSM road and building data in the Stockholm metropolitan area.
An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where supplying the roads and paths with indivdual widths would cause collision with other features.
An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.
\\
It was found that the average positional error in the OSM dataset was about 2 meters, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.
%TODO: Include a summary of the collision run
The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.

@@

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 26473         & 10523        & 3044        & 2756        \\
    Nodes, total            & 6382579       & 6612383      & 968420      & 420810      \\
    Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
    Features, colliding     & 3189          & 1032         & 412         & 456         \\
    Nodes, colliding        & 7330          & 2362         & 643         & 824         \\
    Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
    Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
    Nodes, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
    Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0133 \%

>>>>

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling}

@@

This project assesses the feasibility of creating a 3D representation of OpenStreetMap (OSM) geodata with the inclusion of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.
\\
An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
It was found that the average positional error in the OSM dataset was about 2 meters, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.
\\
This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where extending the roads and paths with indivdual widths would cause collision with other features.
An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
It was found that extending all roads with a standard width led to collisions between roughly 12\% of all roads in the dataset. The total length of road that intersected with other features was less than 0.1\% of the total road length. It was measured that roughly 80\% of these colliding features could be corrected by simple geometrical translation by a distance smaller than the posiional accuracy of the OSM dataset. Similarily, the amount of colliding road by length that could be corrected was calculated to around 99\%.
\\
The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.
As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.

@@

In recent years, there have been an advent of tools that extract geodata from OpenStreetMap (OSM) and generate 3D representations of real world locations by placing terrain, buildings, roads and other features.
However, freely available such tools seldom include smaller roads and pedestrian footpaths such as walkways, sidewalks or trails.

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 26473         & 10523        & 3044        & 2756        \\
    Nodes, total            & 6382579       & 6612383      & 968420      & 420810      \\
    Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
    Features, colliding     & 3189          & 1032         & 412         & 456         \\
    Nodes, colliding        & 7330          & 2362         & 643         & 824         \\
    Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
    Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
    Nodes, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
    Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0.13 \%
